Mendelian randomization for causal inference in Genome-wide association studies

### 2022-02-19 mr-review.Rmd
expanded OMR section

Recent research on the omnigenic hypothesis, which posits 
that every SNP's effect on a trait is nonzero, has informed
MR methods development [@Boyle2017]. @wang_mendelian_nodate 
recognized the limitations of previous MR methods in the 
context of the omnigenic hypothesis. To accommodate the possibility
that a trait is influenced by many SNPs, @wang_mendelian_nodate

>>>>

Recent research on the omnigenic hypothesis, which posits 
that every SNP's effect on a trait is nonzero, has informed
MR methods development [@Boyle2017]. @wang_mendelian_nodate 
recognized the limitations of previous MR methods in the 
context of the omnigenic hypothesis. In response, @wang_mendelian_nodate 
developed a MR method that explicitly uses all genome-wide SNPs as instruments. 
Using GWAS summary statistics as inputs, their method relies on a composite likelihood framework for scalable computation and allows for horizontal pleiotropy. @wang_mendelian_nodate used extensive 
simulations, including those with model misspecifications, to characterize their method's statistical power and robustness. Finally, they applied the new method to 
identify multiple complex traits that affect coronary artery disease and asthma. These causal relationships highlight the important roles of plasma lipids, blood pressure, and the immune system in CAD susceptibility and those of obesity and the immune system in asthma development.
